TBD

### 2021-02-16 outputs/paper/paper.Rmd
Graph labels updated.

ggplot(data = all_simulated_dataset, mapping = aes(x = Q7, fill = type)) + 
  geom_bar(position = position_dodge(1)) +
  labs(x = "X",
       y = "Y",
       title = "Q7",
       fill = "Type") +
  theme_minimal()

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q12, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "X",
       y = "Y",
       title = "Q12",
       fill = "Legend") +
  theme_minimal()

>>>>

ggplot(data = all_simulated_dataset, mapping = aes(x = Q7, fill = type)) + 
  geom_bar(position = position_dodge(1)) +
  labs(x = "Did revenue increase, decrease, or remain the same compared to last month?",
       y = "# of restaurants",
       title = "Q7",
       fill = "Type") +
  theme_minimal()

@@

ggplot(data = all_simulated_dataset, mapping = aes(x = Q12, fill = type)) +
  geom_bar(position = position_dodge(1)) +
  labs(x = "Was there a reduction in restaurant hours?",
       y = "# of restaurants",
       title = "Q12",
       fill = "Legend") +
  theme_minimal()
